## Participation of Enrolled Students

Non-participation^[We assume that being in the data file without a scale score
indicates non-participation. We did not have demographic variables for these
non-participating students and where therefore only able to examine non-participation
by grade, school and district.] may jeopardize our ability to understand performance,
either overall or for some groups of students (e.g., subgroups or schools). In
this analysis of participation we focus on students officially enrolled in the
state^[We assume that being within the data file constitutes enrollment.] and were
therefore expected to test in the spring. In later sections we consider the potential
impact that decreased enrollment ("attrition") may also have on our ability to
understand changes in student performance.

```{r, echo=FALSE}
  ##  Retrieve stats for the next paragraph from the overall_participation_rates table.
  ##  We'll need to work on extending this out for multiple assessments, probably
  ##  as a "child-within-child".

  tmp.assessment <- "State_Assessment"
  tmp.test.abv <- params[["test.abv"]][[tmp.assessment]]
  tmp.participation.table <-
    Report_Analyses[["participation"]][[tmp.assessment]][["overall_participation_counts"]][
      YEAR == tail(params[["years"]][[tmp.assessment]], 1) & LEVEL == "State" & GRADE == "All" & SUBGROUP == "All" & PRIOR_ACHIEVEMENT_LEVEL == "All"]

  tmp.rates <- c()
  tmp.nonpart <- c()

  for (s in params[["GL_subjects"]][[tmp.assessment]]) {
    tmp.rates <- c(tmp.rates, round(tmp.participation.table[CONTENT_AREA == s, PERCENT_TESTED], 1))
    tmp.nonpart <- c(tmp.nonpart, tmp.participation.table[CONTENT_AREA == s, NUMBER_STUDENTS - NUMBER_TESTED])
  }

  ##  Rates
  tmp.partic.rate <- paste(tmp.rates, "in", params$GL_camel[[assessment]])
  tmp.partic.rate <- paste(paste(head(tmp.partic.rate, -1), collapse=", "), tail(tmp.partic.rate, 1), sep=" and ")
  tmp.partic.rate <- gsub("Math$", "Mathematics", tmp.partic.rate)

  ##  Counts
  tmp.partic.count <- paste(prettyNum(tmp.nonpart, big.mark=","), "eligible students in", params$GL_camel[[assessment]])
  tmp.partic.count <- paste(paste(head(tmp.partic.count, -1), collapse=", "), tail(tmp.partic.count, 1), sep=" and ")
  tmp.partic.count <- gsub("Math$", "Mathematics", tmp.partic.count)

  ##  Set up caption for 'Overall Participation' table
  ovrall.part.cap <- paste("Overall", params[["test.abv"]][[tmp.assessment]], "Participation Rates")
```

###  `r tmp.test.abv` Participation Rates

The overall participation rate in 2021 for the `r tmp.test.abv` assessment was
`r tmp.partic.rate`. These participation rates mean that `r tmp.partic.count` out
of `r prettyNum(tmp.participation.table$NUMBER_STUDENTS[1], big.mark=",")` eligible
students did not test.

Table `r tblNum(1)` shows the `r tmp.test.abv` participation rates by grade
and achievement levels.

```{r, overall-participation-table, fig.cap=ovrall.part.cap, out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}
  ###   Overall Participation Table
  tmp_part_tbl <- copy(Report_Analyses[["participation"]][[tmp.assessment]][["overall_participation_rates"]])
  for (v in names(tmp_part_tbl) %w/o% c("GRADE", "PRIOR_ACHIEVEMENT_LEVEL")) {
    tmp_part_tbl[, eval(v) := round(get(v), 2)]
  }
  tmp.ach.lev <- c(rev(params$achievement_levels[[assessment]]), "No Prior Level")
  ovr.indx <- c(which(tmp_part_tbl$GRADE=="All" & tmp_part_tbl$PRIOR_ACHIEVEMENT_LEVEL=="All"),
                which(tmp_part_tbl$GRADE!="All" & tmp_part_tbl$PRIOR_ACHIEVEMENT_LEVEL=="All"),
                match(tmp.ach.lev, tmp_part_tbl$PRIOR_ACHIEVEMENT_LEVEL))
  tmp_part_tbl <- tmp_part_tbl[ovr.indx,]

  rgroup.indx <- c(1,length(which(tmp_part_tbl$GRADE!="All" & tmp_part_tbl$PRIOR_ACHIEVEMENT_LEVEL=="All")), length(tmp.ach.lev))
  cgroup.indx <- c(2, rep(2, length(params[["GL_subjects"]][[tmp.assessment]])))
  cgroup.names <- c("", params[["GL_camel"]][[tmp.assessment]])
	# tmp.caption <- paste("Overall", params[["test.abv"]][[tmp.assessment]], "Participation Rates")

  setnames(tmp_part_tbl,
    sapply(gsub(paste(c(params[["GL_subjects"]][[tmp.assessment]], "[.]"), collapse="|"), "", names(tmp_part_tbl)), capwords))

  ###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(tmp_part_tbl, rnames=FALSE,
			title="", align=paste0('cc', paste(rep('r', ncol(tmp_part_tbl)-2), collapse="")), # rnames = tmp.rnames,
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
			n.cgroup=cgroup.indx, cgroup=cgroup.names,
	    caption=Literasee::tblCap(ovrall.part.cap), css.table="min-width: 85%;"))
```

<!--  
  Not sure if we want to extend the universal text for grades/schools below?
  We'd need to implement a similar strategy for the stats used below as was done above.
  Or add a custom analysis for each state...  
-->

The students who did not participate were more often in higher grades (e.g., in
ELA 349 non-participating students were in grade 8 compared to the 111
non-participating students in grade). Also, students who did not participate were
also were more often in lower achievement levels in 2019 than students who
participated (e.g., in ELA 50.0% of the non-participating students were in the
lowest achievement level, Below Proficiency, in 2019 whereas 28.5% of participating
students were classified as Below Proficiency in 2019).

Non-participation also clustered within certain schools. In ELA out of the 1,799
schools, 447 schools had at least one student who did not test. A smaller number
of these schools accounted for the majority of the students who did not participate.
In ELA, 96 schools accounted for 58.7% of the non-participation. Similarly, for
Mathematics, 115 schools accounted for 62.0% of the non-participation. See Figures
1 and 2 in the Participation Appendix for more detail.
