## Assessment Participation

This section gets at missing data through participation rates.  Some data may need
to be provided by the state.  Another way to get at it would be to check SGP
calculation rates.  This assumes that students we had in the 2019 data should be
present in the 2021 data.  It may be the best we can do...

Table `r tblNum(1)` provides frequencies and proportions associated with student
SGP counts by year, content area, and grade. An important aspect of Table `r tblNum(1)`
is that there are no `r skip.excluded.grade` SGPs because no prior score exists with
which to calculate growth since there is no exam administered two grades prior.
The absence of SGPs for an entire grade level has a significant impact on
comparisons done at the elementary school level.

```{r, echo=FALSE}
# results='asis',
	rgroup.indx <- diff(c(which(SGP_Counts[,1] != ""), (nrow(SGP_Counts)+1)))
	tmp.caption <- "Baseline and cohort SGP counts and percentages for 2019 and 2021 by content area and grade"

  knitr::knit_print(
		htmlTable::htmlTable(SGP_Counts,
			title="", align=paste0('cc', paste(rep('r', ncol(SGP_Counts)-2), collapse="")), # rnames = tmp.rnames,
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
			# tspanner=rep("", nrow(SGP_Counts)/2), n.tspanner=rep(2, nrow(SGP_Counts)/2),
			# rgroups=list(c("ELA", "Mathematics"), ""), n.rgroups=list(nrow(SGP_Counts)/2, rep(2, nrow(SGP_Counts)/2)), # n.tspanner
	    # n.cgroup=c(3, 2, 2), cgroup=c("", "Baseline", "Cohort"),
			n.cgroup=c(4, 2, 2), cgroup=c("", "Baseline", "Cohort"),
	    caption=tblCap(tmp.caption)))
```

Here is an example of how to include tables for counter/caption similar to figures
in pagedown template.  If we go this route Adam will need to put this into a function
to render the table differenly in bookdown than in pagedown


```{r fig.cap="Baseline and cohort SGP counts and percentages for 2019 and 2021 by content area and grade", out.width="0", out.height="0", out.extra='data-prefix="Table"', results="asis", echo=FALSE, eval=ifelse(tolower(params$render.format) == "pagedown", TRUE, FALSE)}

	###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(SGP_Counts,
			title="", align=paste0('cc', paste(rep('r', ncol(SGP_Counts)-2), collapse="")),
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
			n.cgroup=c(4, 2, 2), cgroup=c("", "Baseline", "Cohort"),
	    caption=NULL, css.table="margin-top: -1.25em;margin-bottom: 1em;min-width: 75%;"))
```

Arcu dolor at nullam sed torquent tellus non. Cubilia eget in nisi, penatibus aenean
congue lorem et ornare tristique leo facilisi orci vel. Non varius vestibulum nam
morbi pe llentesque sit. Vitae in eget eu sed elit, et ad lacus, eleifend nisl,
potenti eget egestas. Eros eu porttitor, tristique fames, et pellentesque lacinia
et. Porttitor in etiam ac nec montes. Ante finibus purus neque ante et. Et amet
suspendisse potenti at bibendum vivamus bibendum sapien. Eget egestas pharetra
metus phasellus volutpat non donec sed id.

- Varius, eros, mattis vulputate fringilla dis felis eros. Felis, enim dolor
vestibulum curabitur commodo ex nisi. Duis nostra, nibh condimentum urna curabitur
interdum mauris, dui, ac.
- Faucibus mus semper tortor justo ut ornare vel consectetur ipsum. Sed nunc vel,
taciti, eu urna neque ut habitasse sed ipsum dis sed faucibus. Leo donec vel, varius
ac tortor at. Etiam leo egestas maecenas purus eros ultrices iaculis.
- Tempus imperdiet dis sed nunc ut. Sed sit convallis lacus neque habitant id id
posuere nostra. Ligula convallis nec vitae. Eget himenaeos sit purus sed mauris
pellentesque lorem sollicitudin nisl.
- Dolor amet et dictum ad elementum, sed, sed nibh turpis. Nunc id cubilia dolor
mauris, vestibulum nulla odio venenatis leo dignissim. Eu egestas semper porttitor.
