## Replacing Missing Scores

The key question around non-partipcation is whether it jeopardizes our understanding
of student performance. One simple way to check whether non-participation could
impact our overall conclusions is by replacing the missing scale scores and achievement
levels of students who did not participate. An extreme approach is to replace
these missing values with lowest possible scores and levels, or the highest possible
scores and levels. A less extreme approach is to replace scores and levels with
those the non-participating students were likely to receive based on their prior
performance. This less extreme approach involves determining what scores and levels
are likely for each student, based on methods like regression. Here we avoid the
methodological complexity involved in this less extreme approach, and instead
simply replace missing values – once by replacing the missing values with the
minimum obtained score and level per grade, and then again by replacing the missing
values with the highest obtained score and level. For each replacement, we then
compute school- and state-level mean scale scores and percent proficient, then
compare to the observed scores.

Table `r tblNum(1)` shows the worst and best case scenarios in school mean scale
scores when replacing missing test scores with the minimum and maximum scores.

```{r, minmax-mss-state, fig.cap="State-Level Mean Scale Score, Before and After Replacement with Minimum and Maximum Scores.", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}

  tmp.assessment <- "State_Assessment"

  ###   State-Level Min/Max table: Mean SS
  minmax_mss_state <- copy(Report_Analyses[["participation"]][[tmp.assessment]][["state_minmax_diff_mean_pctp"]])
  minmax_mss_state <- minmax_mss_state[, list(
    CONTENT_AREA, GRADE, MEAN_SCALE_SCORE, SD_SCALE_SCORE,
    MEAN_SCALE_SCORE_altMIN, MEAN_SCALE_SCORE_minDIF, MEAN_SCALE_SCORE_altMAX, MEAN_SCALE_SCORE_maxDIF)]
  setkey(minmax_mss_state, CONTENT_AREA, GRADE)
  for (v in names(minmax_mss_state) %w/o% c("GRADE", "CONTENT_AREA")) {
    minmax_mss_state[, eval(v) := round(get(v), 1)]
  }

  rgroup.indx <- unlist(lapply(unique(minmax_mss_state$CONTENT_AREA), function(f) length(minmax_mss_state[CONTENT_AREA==f, GRADE])))
  cgroup.indx <- c(4, 2, 2)
  cgroup.names <- c("", "Minimum", "Maximum")

  minmax_mss_state[, CONTENT_AREA := gsub("ematics", "", sapply(CONTENT_AREA, capwords))]
  minmax_mss_state[which(duplicated(CONTENT_AREA)), CONTENT_AREA := ""]

  setnames(minmax_mss_state, names(minmax_mss_state)[1:4], c("Subject", "Grade", "Observed", "SD Observed"))
  setnames(minmax_mss_state, grep("_alt", names(minmax_mss_state), value=TRUE), c("Replaced", "Replaced"))
  setnames(minmax_mss_state, grep("DIF$", names(minmax_mss_state), value=TRUE), c("Observed-Replaced", "Observed-Replaced"))

  ###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(as.matrix(minmax_mss_state), rnames=FALSE,
			title="", align=paste0('cc', paste(rep('r', ncol(minmax_mss_state)-2), collapse="")), # rnames = tmp.rnames,
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
			n.cgroup=cgroup.indx, cgroup=cgroup.names,
	    caption=Literasee::tblCap(knitr::opts_current$get("fig.cap")), css.table="min-width: 85%;"))
```


```{r, minmax-pctp-state, fig.cap="State-Level Percent Proficient, Before and After Replacement with Minimum and Maximum Scores.", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}
  ###   State-Level Min/Max table: Percent Proficient
  minmax_pctp_state <- copy(Report_Analyses[["participation"]][[tmp.assessment]][["state_minmax_diff_mean_pctp"]])
  minmax_pctp_state <- minmax_pctp_state[, list(
    CONTENT_AREA, GRADE, PERCENT_PROFICENT,
    PERCENT_PROFICENT_altMIN, PERCENT_PROFICENT_minDIF, PERCENT_PROFICENT_altMAX, PERCENT_PROFICENT_maxDIF)]
  setkey(minmax_pctp_state, CONTENT_AREA, GRADE)
  for (v in names(minmax_pctp_state) %w/o% c("GRADE", "CONTENT_AREA")) {
    minmax_pctp_state[, eval(v) := round(get(v), 1)]
  }

  rgroup.indx <- unlist(lapply(unique(minmax_pctp_state$CONTENT_AREA), function(f) length(minmax_pctp_state[CONTENT_AREA==f, GRADE])))
  cgroup.indx <- c(3, 2, 2)
  cgroup.names <- c("", "Minimum", "Maximum")

  minmax_pctp_state[, CONTENT_AREA := gsub("ematics", "", sapply(CONTENT_AREA, capwords))]
  minmax_pctp_state[which(duplicated(CONTENT_AREA)), CONTENT_AREA := ""]

  setnames(minmax_pctp_state, names(minmax_pctp_state)[1:3], c("Subject", "Grade", "Observed"))
  setnames(minmax_pctp_state, grep("_alt", names(minmax_pctp_state), value=TRUE), c("Replaced", "Replaced"))
  setnames(minmax_pctp_state, grep("DIF$", names(minmax_pctp_state), value=TRUE), c("Observed-Replaced", "Observed-Replaced"))

  ###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(as.matrix(minmax_pctp_state), rnames=FALSE,
			title="", align=paste0('cc', paste(rep('r', ncol(minmax_pctp_state)-2), collapse="")), # rnames = tmp.rnames,
			tspanner=rep("", length(rgroup.indx)), n.tspanner=rgroup.indx,
			n.cgroup=cgroup.indx, cgroup=cgroup.names,
	    caption=Literasee::tblCap(knitr::opts_current$get("fig.cap")), css.table="min-width: 85%;"))
```

These analyses can also be extended to the school-level. Table `r tblNum(1)` below
summarizes these differences at the school-level, for schools with more than
fifteen students who also had at least one non-participating student.


```{r, minmax-school-qtlss, fig.cap="School-Level Mean Scale Score Differences (Observed – Replaced) by Decile.", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}
  ###   School Quantile Table 1 - Mean Scale Scores
  minmax_school_qtlss <- copy(Report_Analyses[["participation"]][[tmp.assessment]][["school_minmax_diff_quantiles"]])
  minmax_school_qtlss <- minmax_school_qtlss[variable %in% c("MEAN_SCALE_SCORE_minDIF", "MEAN_SCALE_SCORE_maxDIF")]
  setorderv(minmax_school_qtlss, cols=c("variable", "CONTENT_AREA", "GRADE"), order = c(-1, 1, 1))
  for (v in names(minmax_school_qtlss) %w/o% c("GRADE", "CONTENT_AREA", "variable")) {
    minmax_school_qtlss[, eval(v) := round(get(v), 1)]
  }

  rgroup.indx <- minmax_school_qtlss[,.N, by = c("CONTENT_AREA", "variable")][, N]
  cgroup.indx <- c(2, 9)
  cgroup.names <- c("", "Mean Scale Scores (Observed - Replaced)")
  tspanr.indx <- minmax_school_qtlss[,.N, by = "variable"][, N]
  tspanr.names <- c("Missing Scores Replaced With Minimum Scale Score", "", "Missing Scores Replaced With Maximum Scale Score", "")
  minmax_school_qtlss[, CONTENT_AREA := gsub("ematics", "", sapply(CONTENT_AREA, capwords))]
  minmax_school_qtlss[setdiff(1:nrow(minmax_school_qtlss), c(1, 1+head(cumsum(rgroup.indx), -1))), CONTENT_AREA := ""]
  minmax_school_qtlss[, variable := NULL]
  setnames(minmax_school_qtlss, names(minmax_school_qtlss)[1:2], c("Subject", "Grade"))

  ###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(as.matrix(minmax_school_qtlss), rnames=FALSE,
			title="", align=paste0('cc', paste(rep('r', ncol(minmax_school_qtlss)-2), collapse="")),
      # n.rgroup=rgroup.indx, rgroup=rep("", length(rgroup.indx)),
      n.tspanner=rgroup.indx, tspanner=tspanr.names, css.tspanner = "text-align: center; font-weight: 600;",
			n.cgroup=cgroup.indx, cgroup=cgroup.names,
	    caption=Literasee::tblCap(knitr::opts_current$get("fig.cap")), css.table="width: 100%;"))
```


```{r, minmax-school-qtlpctp, fig.cap="School-Level Percent Proficient Differences (Observed – Replaced) by Decile.", out.width="0", out.height="0", out.extra=tab.out.ex, class = "figtab", results="asis"}
  ###   School Quantile Table 1 - Mean Scale Scores
  minmax_school_qtlpctp <- copy(Report_Analyses[["participation"]][[tmp.assessment]][["school_minmax_diff_quantiles"]])
  minmax_school_qtlpctp <- minmax_school_qtlpctp[variable %in% c("PERCENT_PROFICENT_minDIF", "PERCENT_PROFICENT_maxDIF")]
  setorderv(minmax_school_qtlpctp, cols=c("variable", "CONTENT_AREA", "GRADE"), order = c(-1, 1, 1))
  for (v in names(minmax_school_qtlpctp) %w/o% c("GRADE", "CONTENT_AREA", "variable")) {
    minmax_school_qtlpctp[, eval(v) := round(get(v), 1)]
  }

  rgroup.indx <- minmax_school_qtlpctp[,.N, by = c("CONTENT_AREA", "variable")][, N]
  cgroup.indx <- c(2, 9)
  cgroup.names <- c("", "Percent Proficient (Observed - Replaced)")
  tspanr.indx <- minmax_school_qtlpctp[,.N, by = "variable"][, N]
  tspanr.names <- c("Missing Achievement Levels Replaced With Not Proficient", "", "Missing Achievement Levels Replaced With Proficient", "")
  minmax_school_qtlpctp[, CONTENT_AREA := gsub("ematics", "", sapply(CONTENT_AREA, capwords))]
  minmax_school_qtlpctp[setdiff(1:nrow(minmax_school_qtlpctp), c(1, 1+head(cumsum(rgroup.indx), -1))), CONTENT_AREA := ""]
  minmax_school_qtlpctp[, variable := NULL]
  setnames(minmax_school_qtlpctp, names(minmax_school_qtlpctp)[1:2], c("Subject", "Grade"))

  ###  Include VERY small, transparent image to create table title and
	knitr::include_graphics("data:image/gif;base64,R0lGODlhAQABAIAAAAAAAP///yH5BAEAAAAALAAAAAABAAEAAAIBRAA7", dpi=NA, error = FALSE)

  knitr::knit_print(
		htmlTable::htmlTable(as.matrix(minmax_school_qtlpctp), rnames=FALSE,
			title="", align=paste0('cc', paste(rep('r', ncol(minmax_school_qtlpctp)-2), collapse="")),
      # n.rgroup=rgroup.indx, rgroup=rep("", length(rgroup.indx)),
      n.tspanner=rgroup.indx, tspanner=tspanr.names, css.tspanner = "text-align: center; font-weight: 600;",
			n.cgroup=cgroup.indx, cgroup=cgroup.names,
	    caption=Literasee::tblCap(knitr::opts_current$get("fig.cap")), css.table="width: 100%;"))
```
